### 2015-05-15 evaluation.tex
fix

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral times out in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some of its entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization. This shows that \whoop has value as a stand-alone analyzer.

>>>>

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral times out in all configurations (with and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some of its entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization. This shows that \whoop has value as a stand-alone analyzer.
